\h{Master and Apprentice}

The touge race has just begun. And the crowds along the mountain path cheered on the three drivers who are now racing each other. The blue Subaru is currently in front with the red Evo and Green Skoda closely behind. There are tight turns from start to end of the course but none of them has gained a clear advantage so far.

Rest of the crew is spread along the entire course watching their every move, communicating with each other while listing signals from Lancer and Nekomi.

The other two co-drivers of Kimi and Pierre stood a few corners down the road.

"So far no problems so far. But I am starting to hear them approaching now." Pierre said.

"Alright, currently signals are still stong." Alice replied, "Keep an eye on the blue one by the way, she's our current target."

The voices of engine roaring become closer and closer and three pair of light appear among the trees. There they come, appearing on their sights after a quick left turn, starting to go downhill and all smoothly drifted a right hand turn in front of their eyes. Then the sounds slowly fade away. Witnessing a touge race is like spectating a rally race, one second they are there and the next they are gone. All that celebration is just for one moment of cars going quick in front of your eyes.

"Number 41 is within close range of target." Kimi responded, "Almost within touching distance."

Meanwhile inside the cockpit of Nekomi's car. He finally heard a call-out from Lancer. "In a few turns the road will widen itself, we shall make a quick move then."

"OK." Nekomi swiftly responded.

"But you make the call alright?" Lancer then said.

"Why?" Nekomi then asked.

"Just shut up and do it! Ask later!" Lancer annoying said.

They both turned a couple corners just to wait for the right moment, until there is a wide right turn in front of them. Nekomi goes up the indise of the corner right beside Lancer's red Evo and said, "Me in you out. Now!"

Nekomi and the blue Subaru initiated into a drift parallel to each other, while Lancer gaining grip swiftly goes around the outside corver overtaking both cars.

"Great distraction!" Lancer commented.

After Nekomi took the better line, he overtook the blue WRX on the corner exit as well. The crowd cheered. Angelina and Liana just so happen to be right at that wide corner, not only saw everything, but heard the things that went down was amazed by the result.

Angelina then said, "Well, the lack of snow does makes things easier."

Liana then said, "He sure have improved quite a bit since he came to the Alps."

Angelina then replied, "Yeah, no matter what happens next, at least this is going to be a good race."

Both Nekomi and Lancer thought things has went smoothly, but then they witnessed a corner just after a uphill section. Lancer while at front took that sharp turn by surprise, lost balance of her car and slipped. Nekomi is also shocked to see that happen, had to brake early, although Nekomi is able to recover both were overtaken by the 'Mountain Shogun' in her blue Subaru.

Nekomi got a bit fustrated but also a bit helpless.

"My bad, haven't been in those mountains for quite some time, I seemed to show my age there." Lancer explained but Nekomi simply grunts through his earpiece. "You did initiate a good move there, its on you now."

"Everyone makes mistakes, keep our head low, we persevere." Nekomi then said, "Thanks for you help but I think its best to do it all by myself." Then he puts down his head piece to focus on the race.

"I'm going to take this chance to see how they both drive, just wanted to see if my thoughts are right." Lancer thought to herself.

The rest of the crew listening in just heard that they just missed a really great oppurtunity. However in the sea of data that Alice got earlier, she got some surprising results.

"After compiling scources from street racers, they are currently three seconds ahead of stage record. If this continue... Oh my!" Alice reported.

Mason is surprised to hear that and asks further, "Then who held the previous record?"

"Its the 'Mountain Shogun', it seems that even our target is pushing it." Alice continued, "We may be seeing what our target is capable of. This is definitely going to be useful to our current database. It seems that you can do a lot with around 300 horsepower."

All three cars are now in a fast but twisty section, precise controls are required to make those turns. This terrain totally suits Lancer's car with a sophisticated YAW control system but the other two cars seem to be going fine. Right at the end of this fast section there is a slightly sharper turn that could potentially throw some amateurs off.

Both Clara and her cousin Cossie is on a hill overlooking that part of the road. Hearing all the noises blaring beneath them.

"Alright they are all flawless in their turns so far. Just keep moving up and down side to side like a..." Cossie reported to the rest of the team.

Lancer then innterupted her saying then said, "That is what I'll do but for the other two, we'll see."

In front of Lancer, as Nekomi and the blue Subaru going to the final part of this section, barely slow down at all, and just when the barriers are gone, they both got their right wheels into the grass and dipped below the road for the left turn before the sharp right.

"Watch out!" Clara exclaimed as they both exited the grass, which kicked up the left side of their cars, shifting the balance towards the corner, landing facing the straight. The locals called this the corner jump, word on the street has it that the 'Mountain Shogun' invented this local trick and other street racers have attempted and failed to do so.

An outsider somehow manages to succeed at the first try, makes the crowd go wild, but a hint of suspicion is in the air.

"Well that's all I need to know to confirm my hypothesis." Lancer then said to the rest of the team.

"What was that?" Clara explained, "Only the craziest drivers will do such things?"

Mason unable to see the insanity that just happened, scrambled to try to figure out the current situation.

Alice is now even more surprised and said, "Jumping that corner is three tenths a second faster than my model suggests."

"Wanna try to compare data between number 41 and target please. Just to confirm." Lancer then said.

Alice typed on her laptop, shocked with the results with both hands covering her mouth, exclaimed, "Gott im Himmel!"

Mason immediately rushed to her laptop to figure out what's wrong.

"They both have a match of 90\%, with a p-value of 0.01." Alice mutterd in shock.

"I knew this since I saw the way he drives." Lancer explained. "This is not just a race to chase one of the most mysterious 'car spirits', nor its about to defeat one of the most legendary street racers out there."

"Wait, wait, wait hold on!" as Clara jumps into the call, "Has the situation changed at all?"

"How did he even do that." Margarita also jumped into the call near the end of the stage with Camilia beside her. "Its almost a perfect match!"

"It is a perfect match Delta." Alice explained, "The null hypothesis is clearly been rejected here."

"He is definitely mimicing her moves to achieve such speeds." Clara then tried to elaborate.

Mason then goes against her and said, "No he is literally driving like usual here. I am the guy sitting next to him, I can tell."

"This can only mean one thing." Lancer then explained. 

\hfill

"This is a race bewteen the master and her best apprentice."

\hfill

The rest of the team was in shock by what Lancer just said. Then Lancer further states that, "The master hidden in all his dreams, all of his fading memories, is the 'Mountain Shogun' herself."

