\h{Blue}

His eyes slowly opened up, things were blurry at first but it slowly got clearer in front of him. He looked around his surroundings, looks like he is in a seat of a car of some sort, trapped in a seat belt, too fatigued to even move around his seat. 
Looking across the black dashboard of the car he is in, he sees a woman with a long blue ponytail with a blue baseball jacket, driving calmly.
Looking closely at her, she has two star shaped hair clips each on her side, and on her outfit, there are lines of yellow decorating her look. 
After some analysis, it is clearly the 'Mountain Shogun'.
She then took a glace towards himself, continued to took at the road in front of her, opened her mouth then said, "I'm glad you're awake."

Nekomi remains seated, then softly muttered, "T...Thank You..."

"I was just going to send you to the hospital but since you seem fine I think its time to find a nice place to talk, just between the two of us." She then said, "Also, let me remind you. Currently, you owe me three things."

"Well, I think I at least owed you my life there." Nekomi then smiled.

"That's one for starters, but lets hold on this conversation until we go somewhere nice. Just take a rest for now, and enjoy the scenery."

As the 'Mountain Shogun' slowly goes up the mountain roads, Nekomi regains his strength, started to sit straight and started to stretch himself.

"Be careful, don't do any sudden movements OK? You don't want me to see to lose another one do I?" she then jokingly said.

Then she parked her car on top of a hill, a small parking lot with a viewing point and two vending machines at the side. They both got out of the car, Nekomi then sat on the bench while the woman went to the vending machine for some drinks.

"I am getting coffee, what do you want?" she asked.

"Marble soda will do." Nekomi responded with slightly recovered energy.

She then returned, sitting next to Nekomi, with the stars shining above and lines of winding lights criss-cross through the mountain, those are the mountain roads that Japan is famed for, and some of them are parts of the course that they just raced through.

"It was fun isn't it?" the woman then said.

Nekomi simply responded by nodding his head, while making a sound of affirmation.

"There are two more things that you still owe me you know." she then said, "The other one, you just promised me earlier, that when you lose, you will have to do whatever I want."

"But that was just a mechanical failiure..." Nekomi said as he got a bit embarrassed at that fact, with her continued, "An L is an L. And you're going to have to stay with me for longer I'm afraid."

"But..." she then said, "I am impressed with your driving, so you can ask me any question you want."

Nekomi thought for a while, with her continued, "Yes, even about the one you are looking for."

Nekomi turned his head towards her then asked, "So why did you slow down for me?"

The woman paused for a second, unable to believe that is what he asked first, then laughed at his question, "Really? Your first question is to question my performance? You're really funny."

"I'm being serious!" Nekomi tries to explain, "I thought I was going to lose there but you somehow opened a window of opportunity at the last second, isn't that a bit suspicious?"

After laughing her heart out, she then said, "Well I was really having tire problems at the later stages. You genuinely have pace over me. Besides, if not for the mistake from Lancer, you would have ran away. You've gone quick."

Nekomi blushed red looked down on his marble soda with both hands holding it, then said, "Umm... Thank you."

"You're nice and shy, but curious at the same time, it makes you cute, just the way I like it." she then complimented.

Nekomi got revealed his cat ears and tail at this moment, the woman chuckled, and continued, "And just the way you used to be."

Nekomi just noticed the way she says things, grew even more suspicious. Looked at the blue haired woman wondering about the words she said to him.

"Oh yeah! I almost forgot, the third thing that you still owe me." she said, "But by the look of your face, I think you are starting to get the hint by now."

Nekomi then remembered what flashed through his mind back then, and asked, "Mountain Shogun?" 

"Yes darling?"

Nekomi slowly wondered, "I was wondering... wait where is my sketch book?"

"Oh you mean this?" The woman said as she took out a large black sketchbook. 

"Did you take a peek in it?" Nekomi immediately yelled.

She then teased him, "Hmmm... maybe."

"What do you mean maybe?" Nekomi yelled again as he got even more embarrassed. 

"You know just a few pages I suppose..." She said as she rolled her eyes to the other side "its good art tho."

"GIVE IT BACK! ITS SUPPOSED TO BE A SECRET!" Nekomi yelled as she snatched the sketch book back into his hands. 

"Alright! Alright! I get it now geez!" she said as she try to calm him down. "Then why can't the person who the artist is drawing have a look how is she drawn tho..."

Nekomi again heard what she just said, then has a feeling that he managed to connect all the dots in his brain. 
Suddenly got a bit nervous, "So... uhh I was wondering that..."

He then finally came forward to her and asked one simple question.

"Were you my master all along?"

She then got up then walked in front of Nekomi, reaching both hands towards him, and gently said, "Alright you got me. I'm done messing with you. Welcome home darling!"

Nekomi slowly realises that the one standing in front of him was his master, the one that taught her everything, the one shred of memory that kept him going, the one that he is looking for during the whole journey. He slowly got up, eyes getting wet, he blurted out saying, "...Master..."

"Don't call me that, we are close friends after all, just call me Subaru-chan, or..."

Suddenly, like a spark that lights a fire, he remembered all the things in his past, as a lot of nightmares overwhelm his mind, but just as he was about to go insane, he also remembered all the pleasant things done by his Master. 
At this moment, his mind just stopped, as he felt a sense of comfort that he has been craving for so long.
Now as he is in between her arms, he slowly looked up to his Master and said.

"Onee-san?"

"Just the way things are supposed to be." as the 'Mountain Shogun' hugs Nekomi tight in her arms with her best apprentice Nekomi crying profusely on her shoulders.

"The third thing you owe me my sweet, sweet darling." she said.

Its been so many years since Nekomi has cried like that, and it is his first time in his life that the fluids coming out of his eyes are tears of joy.
Feelings that have been holding up for years got out like a broken dam, flooding out onto her jacket.

"Just cry on my shoulder all you want, I can tell you have been through a lot Nekomi." she gently whispered while slowly patting his back, "Don't cry! Onee-san is here."

For Nekomi, under the starry sky, above the mountain roads, time has seemingly stopped and rewound back in time to a period where he dearly missed. He holds on her jacket tighter and tigther, unwilling to let go, keeps on murmuring "Onee-san" while surrounded by Subaru-chan.

"Oh dear! You missed me so much. Calm down now, I'll bring you to my place now, alright darling?" She said as she carries Nekomi again towards the passenger seat.

When they both sit down in the car, she poked a finger on Nekomi's cheek. "Boop." She said which causes Nekomi to giggle.

"There, there, lets get you back home." She said as she continues her journey along the mountain roads.

Surely, Nekomi is finally in the right hands right now.
