\h{A Familiar Face}

Nekomi stood on the side of his green and white Skoda, clenching his fists, ready for battle. However this time things are very different. He has dealt with many of the "car spirits" before, but this time he felt a sense of unease, a sense that something is different, something is off, or even something bad is about to happen. His body is trying his best to hide his nervousness but a person with an attention to detail can notice it.

In front of him is his rival, a tall women with a long pony tail, wearing a baseball jacket with side striped shorts, all in blue with streaks of golden yellow as lines on her clothes. Her hair piece is a four angled star each side of her bangs, and the seem to glow like one too. The stood at the side of her blue Subaru, radiating with confidence, facing towards the shy Nekomi.

The woman is a mysterious one, rarely appearing in the twisty mountain roads that they currently on. Whenever she appears, she has the ability to manoeuvre the entire touge with great handing, gaining her the nickname the "Mountain Shogun". There is the saying goes that she only duels with people that she seem worthy, so being able to race with her side by side is an honour by itself.

Nekomi being practically an outsider, and the fact that she previously beaten his teammates Sebastien and Kimi a bit earlier, she is confident to beat him as well.

His pose isn't helping either, with his body wanting to curl into a ball, makes part of the crowd that are hopefull about him winning become doubtful.

The woman decide to further intimidate him by leaning forawrd to Nekomi and pushed her right arm against his green Skoda.

"You scared kid?" She said in a firm voice.

Nekomi turned his head by 45\textdegree, with his eyes looking away from the tall woman in front of him. His four yellow head bands, two on each side of his head, given by his 'Master' when he started to learn racing, glowed underneath her shadow.

Knowing that his 'Master' is beside him at all times, he glanced at the woman and nodded his head, and let out a "M-hm".

"I expected more from the so-called 'Tarmac Specialist', you definitely need to work on your 'Track Anxiety'." The woman said. "Let me guess, I bet you're looking for someone."

Nekomi look straight back at the woman shocked. Unable to believe that she guess what comes to his mind.

The woman chuckeled for a second then said, "It seems that my ears are still as good as ever. I have been hearing your friends about your problem while comming here. So tell me, who are you really looking for?"

"Well..." Nekomi said slowly as he looked behind towards his car, "Someone who taught me how to drive I suppose... Someone who inspired me... I always wante to thank her but I forgot who she is..."

"Hey if she is so important to you, then how come you forgot who she is, isn't she meant to be important to you?" The woman then questioned.

"Well I lost my memory, and I am trying my best to remember really..." Nekomi mutterd.

As he spoke his hair bands seem to slightly glow brighter, the woman immediately notices it and glaces at the glowing hair bands.

"Oh I see now..." The woman said "You know what, if you manage to beat me, I will help you find the person you are looking for."

Nekomi the swiftly asked, "But what if I lose?"

She than said, "I'll guess you have to do whatever I want." As the slowly went to the other side of the car and opened the door. "Chop-chop, the sun is going to rise soon, be prepared alright?"

Nekomi opened his own car's door as well. Right before the woman gets into the car she called at Nekomi, causing him to turn around his body.

She than said, "Hey, one more thing. Be proud of yourself, I know you can do more than you think you can. Darling."

"Darling?" Nekomi thought to himself, "What is she even thinking? She don't know who I am... Right?"

As Nekomi sat down in his car, Lancer came by leaning towards the driver side window, trying to tell some words of engouragement into his ear.

"Alright, throw everything that she said outside your brain, she always try to intimidate her opponents to try to keep them guessing." Lancer said, "She's fast, but as one of the few people that can manage to kick her ass in the past, its totally possible. Just do your thing, it will be all good."

All of a sudden the 'Mountain Shogun' lowers her car window and said, "Hey! Lancer! I haven't seen you in quite some time, wanna spar?"

The crowd start to get intrigued this, Lancer stood facing her. Looked the crowd around her, thought for a while, then said, "You know what? I've been thinking the same."

Now the crowd got excited for an age old rivalry, between a Evo and a STI. Rest of the crew was shocked to hear that happen.

"I know you have been street racing but this is you know... your nemesis." Celica said with a worrying voice

"I know what I am dealing with here, besides I am here just to test my hypothesis." Lancer responded, "Hey nerd! Get as much track data from the three of us."

"Got it!" said Alice.

"Mason! Prepare all communication systems between all of us."

"Alright!" Mason replied.

"Check-check, Nekomi can you hear me?"

"All clear!" Nekomi said.

"Now, Kimi, Seb. Watch and learn."

"Nekomi, I think you're right, I think there is something sus going on around here. I will make sure things are in check, listen to my calls, we gonna do this." Lancer then said as she goes into her Mitsubishi Evo. Nekomi nodded his head in response.

Everyone around the mountain road cheer for this great race, with three cars which include two of the drivers having great 'Street Cred'.

But Nekomi alone in his car, without his trusty co-driver and best friend beside him, isolated against all the noises and fanfare from the outside. Closes his eyes for a moment, catches a deep breath, with his hair bands given from his 'Master' gently glowing in the darkness of the cockpit, giving him a sense of hope. 

"Master... I really wish you can help me right now..."

He tries to remember back when he was younger, remembered one time when he was too nervous, a gentle girl, telling him to calm down with her gentle voice, which she said, "Close your eyes, take a deep breath, and everything you worry about will slowly go away."

But then he was awake from a voice from Lancer, it is being communicated through his head piece. "Listen up small guy, we have a serious race going on tonight. Be prepared."

Nekomi sat back stright, hands on his wheel, with a guy in front of him getting ready to count down, eyes focused on the road. "Ready!" Nekomi said.

"I repeat, don't think too much. The road is all you should care about." Lancer repeated herself. 