\h{Outshining the Master}

Currently in Nekomi's Skoda, staring at the back of the Subaru of the 'Mountain Shogun'. He always feel like he is getting very close to her but yet he can't find a way to overtake the WRX. In a while he genuinely feel that he is going to lose this one and have starting to space out.

But then a memory suddenly popped into his mind. Back when he was still with his master, sitting side by side on the side of a river bank.

He was looking at the scenery, exhausted. Then he heard a soft voice from his master said to him. "Don't do things because you want to succeed, you will face failure no matter where you go."

"Then if there is no success then what should I do?" Nekomi asked.

"Do things for the process." She then continued, "Do it for the sake of it, for the love of it."

Later she added, "Aiya, you always compare yourself to others, but you're not them. Its not even an equal and fair comparison. Remember this: 'Comparison is the thief of all joy". All you need to compare is yourself."

Then he felt a hand touching his back, he looked over towards his master. He saw a girl, slightly taller than him, with a blue ponytail, who then gently said to him, "I am going to leave you soon, try to remember this alright? Darling!"

Nekomi then thought to himself, "Is that... Forget it, there is only one way to find out."

He regained his focus, hands tighten on the wheel, getting prepared to slide into one corner at a time. Beacuse this is the way he likes to drive.

Tires screeching from both cars can be heard all across the mountain roads with another car a bit behind both of them. Margarita and Camilia stood in one section of the road where there are five consecutive tight hairpins, one after another.

"So you telling me that cutie got his driving from, out target?" Margarita in the call trying to confirm.

"It seems that it is." Alice answered, "Try to look closely, they are comming right about now."

Then four dots of bright light emerge from the trees, there they come. A Subaru WRX STI cosely followed by a Skoda Fabia Rally2. They are both getitng into the first tight hairpin. Both tucked at the inner side of the corner, both got wheels deep in the rain gutters. Same strategy, same philosophy, same school of thought. Both trying to use the same way to gain time from one another, eerily in sync.

"They are like two peas in a pod." Camilia thought to herself, "Its like siblings separated at birth."

This continued on for the next corner, and after the other. All five tight hairpins, all using the same method to attack a corner.

"They are now 8.1 seconds ahead of record time." Alice exclaimed, "They might even destory the record by around 10 seconds."

Mason got worried at the speeds that they are acheving in those tight roads, worry things may start to get dangerous.

"This is ridiculus" Mason yelled though the headset.

"I told you things will get tense." Lancer said, "I promise I will keep an eye on both of them."

Near the end of the track there is a wide long left turn, this could be key to whoever that comes first in this race. Tommi and Seb is overlooking this section.

"Who is going to win?" Seb asked, "Wanna bet?"

Tommi remains silent, looked at Seb for a moment and continues to look over the road.

"Hey come on can you at least say something for once." Seb said.

Tommi then put a finger at Seb's mouth then hushed, "Shhh... Listen closely, they are comming."

Both now start to appear in front of their eyes. So close in fact that look like they are going to touch each other. The blue Subaru is holding the inner corner preventing to be overtaken. So Nekomi have to speed around the outside, going side by side into the turn. Then right before they turn, they both braked at the same time, initiated a drift, still somehow manage to stay side by side with one another.

Both Tommi and Seb was amazed by the amount of control both had with their cars. But then the Subaru started to loose grip, swayed to the outside line, which gives way for Nekomi to take the inside like and overtook his supposed master at corner exit.

Tommi and Seb froze from what they have witnessed but after a second of silence, Seb yelled, "Lets go! Nekomi!"

Nekomi pat himself at the chest, for achieving potentially the greatest move of his entire racing carrer. However right before the last corner which is a 90\textdegree turn, his engine decided to fail, bursted into flames, losing control of his car. This led him to crash into the barrier and got into a coma.

Nekomi suddenly being disconnected from the system shocked the rest of the team, some can even able to see the flames emerging, all now in a state of panic.

Luckily Lance manages to follow them just a few seconds before the two, seeing what just appened immediately stopped at the site of the accident.

There she saw the 'Mountain Shogun' herself carrying a little boy on his arms, lifeless but shows signs of breathing, slowly lowering him into the passenger seat of the Subaru.

"Well at least you came." the 'Mountain Shogun' said, "He's a great driver isn't he?"

Lancer nodded her head in response.

"I bet we both know that he doesn't belong to you at this point." the 'Mountain Shogun' continued.

"Can't deny, you raised him well." Lancer responded.

"He's a lovely boy isn't he, didn't grow much since we met." she then said, "At least we got the chance to meet each other and had a fun time, well for the most part."

Lancer simply nodded her head again.

"Tell your new friends that I will take care of this sweet child. We have a lot to talk about." she said as she secured Nekomi with seatbelts and goes back into her blue car.

"Goodbye red head, it was nice to meet you. May we spar again." she said as she close the door.

"Sayonara blue bastard." Lancer responded.

"Just like good old Lancer." she sighed as she closes her window and slowly leaves the scene.

"Well, guess all I can do is to clean up this mess." Lancer told herself as she went back to her car and uses the fire extinguisher that comes with the safety kit to put down the fire from the wrecked Skoda.

The rest of the team finally rushed to the scene, only to find out a burnt car with Lancer standing right beside it.

Mason panicked and yells at Lancer, "Where's Nekomi! Where is he?"

Lancer unfazed and the only person calm with the current situation then said, "He's in good hands right now, I may hate her but I got to admit she is an honest person."

"What you just left cutie into her hands and disappear like that?" Margarita questioned, "How can you just let him go like that."

Lancer replied, "I got my own reasons."

Seb then asked, "Then where is he then? Do you have any idea where she could be heading. She could be heading to Narnia for god knows what!"

"She lives in the mountains, its going to be hard for me to reach her like that. For now, we can do nothing but wait." Lancer further explained. But everyone is still frustrated at Lancer's decision.

But for now, at least one of the largest mysteries in the foundation might have a chance to be solved.
