\h{Project No. 41}

"Wait what!" Michelle yelled after hearing the news of what had just happened back on the mountain roads. 

"In conclusion, car had experienced terminal damage while driver was gone missing." Alice reported. 

"We were catching some big bad blue spirit just to end up with nothing?" Seb then said, "Wait no, not nothing, its negative things! Do you understand how absurd this is?"

"I got nothing to say." Tommi then commented as he lowers his head. 

The whole Japanese base of operations has gone crazy, as they have never had a situation where a person has gone missing during a critical operation, let along concede said person onto enemy territory. At this moment only Lancer seems to have to know half of the whole story, while Mason is trying to wrap his head around the little information provided to all of them. Not only that, what little information found has given more questions than answers. 

"Are you sure that's even her?" Mason yelled, "We barely had any information regarding the Subaru and you have the most information about her in the whole room. And yet you still barely know what's going on, do you know what damage you have caused, do you even care about how we feel, how I feel?"

Everyone seems to keep nagging Lancer regarding this critical moment, trying to find out what has lead to this moment. Lancer took a deep breath, yelled at everyone. "Shut up!"

The whole room went quiet, then Lancer turned towards Mason and questions him, "Do you remember what he had said about the hair bands he was wearing."

"F...From his master." Mason answered, frightened by her loud voice earlier. 

"Those are not just simple decorative hair bands." Lancer continued, "They are hair bands that were given out by the Mountain Shogun to members of the Comet Squad. I knew there is something up when I saw him for the first time. I saw the way he drives. A retard like him can't possibly get this much driving skill just from playing video games."

"Hey! How dare you call him like that!" Josephine yelled. 

"Who cares he's gone!" Lancer continued, "They are a group of highly skilled individuals that either showed great service or great potential under the witness of the Shogun, all handpicked by her one by one. Colin McRae, Richard Burns, Travis Pastrana just to name a few. For the longest time since the inception of your foundation, you guys have simply been borrowing the powers of a member of the special forces without knowing, and even he doesn't realise that."

The whole room went silent after founding out her thought process in all of this. After a quick pause she then proceed to say, "No matter what, every borrowed thing must be returned to its rightful owner, even Nekomi. I was simply following rules and showing respect, I had to let him go."

"But... what will happen to him?" Margarita asked. 

"I think only the two of them knows now." Lancer answered.

Meanwhile is a way less tense atmosphere, in the middle of the mountains. There is the abode of the Mountain Shogun, alone with her apprentice. Celebrating a long awaited reunion. Subie led Nekomi to her living room, both sat on opposite ends of a short table both crossing legs. Nekomi is tired but thankful on what just happened to him and all the things he taught along the way. Subie let out a big yawn and proceeds to sit with him. 

"You seriously did save up all those tears for years just to let it all out on my jacket huh? Jeez you really do miss me" Subie said at which Nekomi nods his head with joy.

"Its not your fault I really missed you too." Subie said as she took off her jacket, revealing her now grown up body. She is now and still is taller than Nekomi and he always have to look up just to face her. But it seems that he now noticed something large on his eye level, which makes him blush a bit and pointed his eyes to the celling to try to not look at her.
However this doesn't mean he has escaped the eye of his master.

"You were looking at my breasts, aren't you?" Subie gently teased and make Nekomi's face turned fully red and he is furiously turning his head left to right.

"Ara-ara! So you did grow up in other ways. But you're still looking, but don't worry I can show you more if you want." Just as Subie said that Nekomi is now covering both his eyes with his tiny hands.

Subie now laughed at Nekomi's reactions and said, "You are still shy as always." She then proceed to calm him down by patting his head, which make Nekomi subconsciously showing her cute cat ears. And now Subie is not only patting his head she is now also rubbing his ears.

"Its alright Neko-kun, I really like you, you know." She whispers as she slowly move her hand across Nekomi's face that led to Subie holding onto Nekomi's cheek. Afterwards, she pulled his little face towards herself, with his whole head totally occupying her view. "Going an entire pilgrimage across the world just to meet the Shogun, do you really miss me that much darling?"

Nekomi's both hands now holding on her arm that is touching his cheek. Leans on her hand a bit, closes his eyes for a moment, then let out a cute little smile. 

"You still remember you have lost a bet and have to do what I say right?" Subie gently reminded him, which subsequently made Nekomi release his hands from her elbow. 

"Hey wait!" Subie then said as she re-grabbed Nekomi's face. "I haven't told you what I want yet."

She pulled his face closer to her for a second time and whispered, "I want you to stay and be my darling is that alright?"

Nekomi's mind paused for a while, just to ended up being smooched on the lips. Just as he realised what is going on, his eyes went a bit wet and nodded his head, "Onee-san" he gently said. 

He then got lifted up, with both his soft thighs being grabbed by both of Subie's arms, pushed against the wall, and she whispered directly to one of his cute neko ears. Saying, "I am going to enjoy this supper very much." followed by a longer kiss. Nekomi wrapped her neck in response. 

And when Subie released his lips, Nekomi has experienced love that he wasn't expecting but it made him to simply say one thing, "I wan't more please." In which Nekomi moved his head towards her just for a deeper kiss, and both started to grab each other tighter than before. 

"You liked it don't you?" Subie then said, "Its getting late now, let me just get you to bed. Let me prepare some milk, then you go take a bath and go to bed alright?" She then put Nekomi back on his two legs and walked into the kitchen. He was left feeling warm after this whole ordeal, but soon he snapped back his mind knowing that as a driver for the foundation he got a duty to fulfill. He immediately, sit back down on the short table, pulled out the notebook in his inner pocket that was used for pace notes, and his pen on the other pocket. Then quickly finding a blank section and starts to record everything he knows about this familiar spirit. 

In the foundation there is a quite interesting naming and numbering convention, driver numbers are skipped for numbering spirit cases, but drivers themselves are allowed to choose a spirit that they like with their own race number. For the longest time, he has been wondering who should that title to be given to, from the past many of them have been considered, from Erika the BMW M3 E30 as being his father's dream car to Margarita the Lancia Delta whose past wounds he helped to heal. And now it seems that his choice was made clear, the one that started it all. 

So he writes down on his notebook, title of the case file. 

"Project No.41"
