\h {Sweet Morning}

The day after the Shogun incident, people in the foundation base has had barely any sleep at all. 
Mason has been waking up in the middle of his sleep multiple time over the potential loss of his best friend, and yet he wants to know more. 

Nekomi has been talking about his once hypothetical master from his past in several occasions, well the word "several" is somewhat of an understatement, its been known and talked about it for so long that, practically speaking everyone has heard of some version of the whole story with varied amounts in detail, and Mason is fully annoyed to see him yap over and over again. 

This story has been investigated and thoroughly disproved in several investigations. 
Even when Alice the nerdy, techy 959 has done a brain scan of Nekomi and done a material analysis on his hair bands has concluded its probably an inner voice of some sort leading him. 
As for a second opinion, the investigative Mini with her assistant Watson the Metro 6R4 has done several interrogations on Nekomi just for them to think that his master is an alter ego in his mind.
If somehow these two experts are not enough, the Lancia family with their underground connections has concluded that no such person exist. 

However, with this new information somehow came along, this case has been widely reopened with Lancer's mere intuition, which further proves her experience as a street racer. 
This news is so unexpected, it has caused everyone with the exception of Lancer or maybe one hopeful side of Mason's brain to have a mental whiplash. 
Not only people were sad to see a tragedy happen, but feelings of frustration and confusion re-emerge surrounding this case.

Lancer woke up to see a half awake Mason, yawning multiple times. 
Being one of the newest member of this group, she barely heard about the story in much detail. 
She got to ask the closest person from Nekomi to ask further details, but right now she needs to make sure he's well awake. 

"Morning Four-eyes, you alright?" Lancer asked.

Mason barely awake drank some coffee, slowly looked at her then continued to drink his coffee. 

"I thought that we need to talk but right now you definitely need that dose of caffeine." Lancer said. 

"Yeah... I figured." Mason murmured, "I got plenty of questions as well."

"You know Nekomi and I know the Shogun. I think we could figure something out if we work together." Lancer then said. 

"Yup, I guess this is what we do now, but please be patient, I need my coffee."

Most of the people belong to the foundation is either frustrated or tired from what has happened... 
Well except for one, the one deep inside the mountains, the one in the abode of the Shogun. 

\hfill

Nekomi opened his eyes, thinking he just had one of the wildest fever dreams he had experienced. 
He thought to himself, "OK... that was weird. But... this ain't my ceiling, this ain't my blanket, this ain't my bed, this ain't my room. Wait, why I'm stuck. Can't make it! Can't make it! This shit's stuck! Outta my way son! DOOR STUCK! DOOR STUCK!"

"Wait! Calm down Neko just try turning your head around and see what's going on." He then thought to himself, by doing so he saw the blue haired girl from yesterday. 

"Oh my god! This is real. Oh my god! I can't wait to prove them all wrong." Just as Nekomi stared at Subie, she slowly opened up her eyes. 

"Hmm? Darling? Its still early, can we sleep for a bit longer?" she then whispered with a smile on her face. 

Nekomi looked around to realised that she has hugged him so tight that he can barely move at all. 

She then whispered, "I felt good last night doesn't it? I did make sure you won't forget about me this time. Want some more?"

Nekomi looked around him, noticing that both of them barely has any clothes on, and his body was filled with kiss marks. 
Remembering all the events that had led him to this point, made him slowly go ahead for the kiss. 
Subie then slowly adjusted the position of both of them, with Nekomi's back against the bed, facing his master, and continued to make love. 
Those years apart, Subie has pent up a lot and Nekomi misses her so much, he just let his master go her way with him and continued in the shower.

After they were done, Subie's lip marks on Nekomi's body had been washed away, but what's left behind are hickeys, nail scratches, bite marks... It has gotten so ridiculous as Nekomi got out of the shower, he turned to his master with a slightly unamused look saying, "Onee-chan, you're such a massive pervert."

"Ara? I may be a pervert but you did eventually ask for more didn't you. Hmm?" Subie gently said as she uses a towel to dry Nekomi's head. 

"You don't have to make my injuries even worse you know." Nekomi replied as he faced forward, but then he slowly looks back at her with a smirk and said, "but... you did made me moan at the top of my lungs so I shall let it slide. Besides, you're still my master after all."

"...and now you understand why this house is deep in the mountains." Subie said as they gently laughed at each other and to get ready for the day.

\hfill

Meanwhile, back in base Lancer-chan got everyone together just to hear what Nekomi had said in the past. 
Staring at everyone who were close to Nekomi, all with concern with the current situation. 

"Alright is it true that Nekomi has been mentioning her all the time?" Lancer then questioned. 

"Yeah he is usually shy and introverted but when she is mentioned at the slightest, he just talks about it non stop!" Seb answered, with Tommi and Kimi nodding in unison. 

"And none, NOT A SINGLE ONE, think that might be true. Not a single one believed him." Lancer then added. 

"I mean I have seen him let his imaginations get over his head. Thinking a simple compliment from a girl would mean he has a chance with her, this is totally what he would do." Mason then said, "He only take words at face value a lot of the time so I had to urge him not to think so in multiple occasions." 

"I have seen him being played on, being taken advantage of from his peers, and it took me dragging him away to make him realise a lot of the time. That's why I urged him to forget this supposedly false memory in order to protect him. There are just too many lies in this world, even though he knows, he is unaware." Mason then continued. 

Josephine then continued, "Dropping hints would never do anything with a guy like that. He sometimes get too suspicious and get not convinced from praises and compliments as he grew up which I can tell. But as a model myself I am happy that there are people out there like him that stays true to what he says, unlike a lot of people in the entertainment industry."

Lancer still as frustrated as before, from the disbelief that no one is willingly to take him seriously to understanding that there are circumstances outside of their control, which arguably causes even more frustration. 
She was going to punch the table but hesitated at the last second, place the same hand on half of her face and sighed,
"I see..." 

\hfill

Back at Subaru-chan's place
