\h{Defying Orders}

In a service park at the end of a rally race, one that is the final race in a championship. It is a place where people not only celebrate the fruits of the whole year, but also for participants to get some rest to get ready for the next season.

This is no different to the team made up of Nekomi Fujiwara (Driver) and Mason Freudenburger (Co-Driver). They have just barely made it into the podium of this rally race by getting third right at the last stage. As rookies for the support series of WRC2, having additional good results not only gives good experience for both of them, they even might catch the eye of the main teams.

However, given the lack of teams in this day and age they would probably prefer to keep their current more experienced lineup instead of getting new recruits. Usually, they will probably be able to stay with the same team for a second year. 

That is... if everything went well... Huge emphasis on the word "if". 

Unfortunately there have been some tensions between the pair and the rest of the team. Also given the fact that Nekomi just disobeyed team orders to fully push the power stage instead of slowing down. Causing the lead driver in the same team to lose out in what could been a close championship fight. Makes the rest of the team unwilling to give out an extension contract.

But its not the fact that Nekomi is being a rebellious young boy trying to go things in his own way, if that's the case Mason wouldn't even bother to support his stance. During the season they found moments in the championship that they were being sabotaged. Times where better quality parts were only given to their teammate and extra parts that belonged to them being used to repair the other car. They both suspect that given the fact that Nekomi was from an esports racing sim background. While Mason, who can barely identify between a Toyota and a Nissan, also had never heard the name Skoda (Which is the car they were driving the whole time) until he hopped into this job practically last minute. Lead to the rest of the team's distrust and discrimination on their abilities. 

In this relaxed environment, there is a whiff of tension in the air, with Mason standing by himself outside the make-shift team office, with muffled noises coming from both the team principal and Nekomi. In a moment after Nekomi went in, he came out marching with a serious look. In which only Mason can tell, something bad has happened. 

"Are we sacked?" Mason asked. 

"Pretty much." Nekomi said as he put both his hands on his waist. 

Mason let out a long breath as he looked at his shoulder, then proceed to continue eye contact. 

"Good riddance!" Mason exclaimed, "I will probably have to beg for a living right now, but at least I can continue to write music. I would much rather live on the street rather than having to deal with these guys."

"Hey disregarding those inbreds back there, you did enjoy this whole rally thing right?" Nekomi then said, "That's why I invited you over after hearing that you were barely scraping by with all those fast-food jobs."

"Yup lots of ideas in my head now." Mason then chuckled, "Getting someone who doesn't know about cars into the racing scene, and somehow getting a trophy."

"Your job is all about timing and tempo, you are a natural!" Nekomi said, "You did a great job today, lets just put this behind us for now and enjoy some champagne we earned."

"Just like what I said back when you were leaving for the UK after all the bullies that you have to deal with." Mason said as he pat Nekomi on the shoulder. "Oh really?" Nekomi replied. 

They both held their own champagne bottles to some chairs within the service park, just to try and enjoy their fruits of their unconventional but temporary success, knowing that they would be out of their job the next day. They both have been together practically since they were kids, two social outcasts fighting a war against the world since they even remember, well only one of them really remembers as Nekomi had suffered a mental breakdown during his school days due to all the social pressure and have practically forgot most of his childhood. So far all he remembers is his family, Mason and maybe his motivation to race. All he knows from his school is that it was terrible. 

After a couple sips of the victory juice Mason then proceeds to check on Nekomi further, "So any visions so far?" He also knows that after that mental episode, he occasionally have visions about his past, lurking at the back of his brain. Sometimes, they were nightmares about his schooldays, but more often than not... well... this is better to let Nekomi explain. 

"Its her again..." Nekomi said as he turned his body around pulling a sketchbook from his backpack. "Its my 'Master' again."

"Oh... of course." Mason sighed, disappointed yet expected. 

"She just told me that we would meet again someday. Again of course." Nekomi said. 

"Yeah yeah..."

"But I think she said that sometimes the end could be the beginning of something greater." Nekomi said as he turned open his sketchbook. 

"Well that's encouraging." Mason then said. 

In his sketchbook, in between the horrors that he drew from his nightmares, there is this blue haired girl, repeated in countless pages with different expressions and poses, with text next to the figures of this girl about his visions and dates of is happening. 

"I don't know why but I have a feeling that she taught everything, and she might be out of this world or something." Nekomi said as he shook his head. "Like does she even exist? Like why does she keep appearing in my sleep over and over and over and over..."

"and over and over and over..." Mason followed, "Yeah... I get it, as an artist I can confirm we are all fried in the brain in one way or another, and its just that we have our own nice little way of expressing ourselves. Honestly, you're no different, I make music while you make art and well... drive, too bad its getting harder to feed ourselves with just art these days. Heck, same can be said hundreds of years ago, all classical composers died early, and its no mere coincidence."

"That's why I even studied engineering in the first place..." Nekomi said, "Born to draw and drive, forced to dy/dx."

They both laughed, took a sip and wondering about what is about to come.

But then a old women approached them, and then asked, "Excuse me is this Nekomi and Mason?". 

"Well of course." Just as Nekomi turned over to the woman, he realised who she was, and yelled, "WAIT ARE YO-"

The old woman immediately covered his hand and put her finger in front of her lips to try and calm him down. 

"What the hell is going on?" Mason said, but unbeknownst to them, there is something out there that will turn the car would on its head.
