\h{The Foundation}

A few days later, Nekomi and Mason are heading to a place at the foot of the Alps in Switzerland, where they agreed to meet the rest of the crew for their first mission. 

"Are you sure that's the spot?" Nekomi asked. 

"It seems so..." Mason said as he repeatedly looked between his map, the address given and the mysterious door in a hole that is fitted into a mountain. 

Still feeling hesitant, Nekomi decided to try knocking on the door followed by Mason pushing the button next to the door. 

"This camera and talking thing should do. Hope we did actually get into the right place or this will get extra awkward."

Weirdly, right before they get any response the big door automatically opened right in front of them. 
Both of them hesitated at first but eventually they slowly entered the door. 
Soon both of them were met with a garage with all the tools and parts needed to fix any problem. 
The garage consists of three cars with Nekomi's Skoda Fabia R5 Evo closest to them,  with a Citroen C3 R5 and a Ford Fiesta R5 Mk.II further away.

"It seems that we aren't the only ones here" Nekomi noted after seeing the inside of the secret garage. 

Right behind the red Citroen with white and grey pattern, there reveals a pair of pink bunny ears peeking at the top of the car. Then a voice appeared. 

"Wait did I hear Nekomi and Mason?" 

Right after that, a person slowly moves from behind the car to the side to reveal himself. 
Showing himself, a bunny boy with a peanut butter complexion and an obvious French accent. 

"Remember me guys?" he said as he let out both his arms inviting both to this place. 

"Sebastien!" Nekomi exclaimed as he reaches out his hand to have a firm handshake and pat each other at the back, with Mason doing the same soon after. 

"So where's Pierre?" Mason then asked. 

"He's just in the bathroom." Sebastien then said. 

Nekomi and Sebastien before in a historic rally back when Nekomi is still a rally racing esports player. He helped him get to know the ways rallying in real life works and try to help him transition from the sim rig to real life. 
From what Nekomi heard, Seb met Pierre back when he was lacking a co-driver due to his original one being sick for an national rally championship while Pierre just so happened to have a similar issue but without a driver. 
By pure accident they both realised that they work better as a team than their original partners hence from then on they decided to team up after the competition. 
Later when both Nekomi and Seb's carrer progressed, they even get to compete against with other, however despite that they still helped with each other from time to time. 

At this point both seemed to be comfortable to reveal their own animal ears with Nekomi having cat ears and Mason having a pair of fox counterpart. 

"So where are the other pair?" Nekomi then asked. 

"Oh you won't believe who also came." Seb exclaimed as he led both of them into the resting area. 
There are sofas with a short table for your legs or food, with a fridge right on the wall. 
Both of them noticed two guys with white hair wearing the same but different coloured clothes, with fox ears on both of their heads. 

Slowly they recognised that both of them belonged to the rival's team from Nekomi and Mason's last rally championship. 

They are the Fubuki twins, half Japanese and half Finnish. 
They both come from a pair of racing drivers, one in super GT and one in rallycross. 
Been racing since they were 5, and had participated in a lot of karting championships. 
However, during their training the co-driver and younger brother Kimi got injured in the skiing accident, losing his left leg, which made Tommi the only one able to advance his racing career. 
As Tommi doesn't want to leave his brother out of the picture, he decided to go into his national sport of rallying and made him his co-driver while being the one driving. 

After hearing both of them appearing, both of them slowly rotated their heads towards them. 
Staring at their soul with a neutral face, with Tommi muttered, "Hi."

"Yeah... they don't like to talk that much." Seb then said. As both Nekomi and Mason proceed to look towards Seb in an awkward manner. 

Tommi then said, "We know why you two are here, we do feel the same."

"Wait what do you mean by that?" Nekomi then asked. 

"I have feeling that I can be faster than my teammate, but due to higher-ups I also have to prioritise my teammate. Seeing you two willing to stand up for yourselves, makes us wanna join in." Tommi then continued. 

"So are we cool now?" Nekomi then questioned. 

Tommi simply nodded his head, reaches out his hand and said, "We work together now."

Nekomi simply smiled and then reached his own hand out to shake his hand. 

Michele then suddenly appeared behind everyone without anyone of them noticing and said, "It seems everyone is getting along well."
Surprising everyone in the room. 

"Don't get too comfortable here, this is all temporary and we got stuff to do." she continued, 
"We are here because we have traced down a good target nearby, if it works, we will have more funding and maybe a shiny new base. So it is important that you guys nail this one, set a good impression to the world what we can do."

"Woah! Woah! Woah! This is all a bit sudden." Seb then said, "We know about the sentient cars situation, but what are we going to do?"

Michele then announced, "That's what I am going to tell you now. Get ready, mission briefing in five minutes."
