\h{Recruitment}

Suddenly, the old woman quickly led Nekomi to a campervan parked on the side of the service park. With Mason being dragged by his curious friend. 

"Hey have you ever heard the saying about the cat that you know... also adding the kind of ears on top of your head, this doesn't look good." Mason said as he followed Nekomi reluctantly. 

"Do you seriously have no idea who she is?" Nekomi said excitedly. 

"Morv please you know I am not into cars that much and honestly she-"

Before Mason can even finished his sentence Nekomi yelled, "ITS MICHELE MOUTON THE QUEEN OF GROUP B."

"Wait who?" Mason confused, causing Nekomi to groan in frustration with him looking at the ceiling and both hands on his face. 

The old woman gently laughed, calmed Nekomi down and said, "Now now young boy, I do appreciate your enthusiasm but I think this would be best if I have introduced myself."

"Hi, I am indeed Michele Mouton, nice to meet you two. I was a rally driver back in the 80s and was the first woman to win a rally. I am currently the president for FIA's Women and Motor Sport Commission."

"Well we aren't women and you have well retired from racing, then why are you asking for... you see... two unemployed guys..." Mason then said. 

"Come on man you are making us look embarrassing in front of DA GOAT here." Nekomi then said to Mason. 

"Let's just say due to unexpected events I got a new job now." Michele said as she turns to her back, grabbing her bag, taking out a light laptop. In said laptop, it started playing a CCTV footage of a car speeding through the city. Both got intrigued while Michele looks at both of their facial expressions, after watching for it for thirty she paused the video asked for comment. "Notice anything?"

"Its an old Ford Escort, produced around the 90s, whale tail, group A homologation. Definitely the RS Cosworth." Nekomi said. 

"Well said, but notice anything about the driving and the driver itself?"

"Well its at least better than the average criminal, probably some street racer." Mason then said, "Wait a minute, hold on, can you please enhance?"

She then enlarge the video towards the windows of the car. Both of them looked through the windows just to notice something, or in this case, the lack of. "There is no driver?" Nekomi then said. 

"I bet this is either AI video or AI driving the car." Mason then said, "But isn't this car..."

"Too old for computers?" Nekomi then said. "Someone must have developed something for it and it is being used maliciously. And it is good at it too."

She then clicked on the laptop for a while just to reveal a series of cases of driverless cars going amok in different parts of the world. 

"These are all videos being circulated around the public. National governments are trying as hard as they do to cover this situation, but only coming back with news of them disappearing or being lost track."

"Then where do we come into the picture?" Mason then said

"Well, what we are thinking is that we need better drivers" Michele then said. "To help catch the baddies obviously."

"But why us?" Nekomi asked, "We suck at this."

"Well racing drivers aren't exactly free are they?" Michele then said, "I've been one, I know. Also, aren't you two got fired and young enough to try something new?"

Nekomi and Mason then stared at each other awkwardly knowing of their situation. 

"I could hire something like a touring car driver. However I think most drivers can only go around in circles, except for rally drivers, they are more likely to adapt to any situation they are given. A co-driver does help too. And given the fact that I am the only person in the executive position in the FIA that can drive rally cars, I have become the lead of this operation."

Both Nekomi and Mason nodded as the finally understand what's going on. "Yeah I do remember seeing those on the Internet" Nekomi then said. 

"So are you willing to join ou-"

"Deal!" Nekomi said as he cut right in the middle of her speech, "We'll join."

"But you haven't bothered with the details yet!" Mason then said as he try to stop the impulsive Nekomi. 

"Hey what choice do we have here, they ain't going to write us a nice cover letter do they?" Nekomi then explained as he stared towards Mason. 

"Oh well fiiiiiiiiiiiiiiiiine, but if this gets anything wrong I am moving back with my parents."
